ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images

### 2023-02-11 paper/paper.tex
minor formatting fixes

\subsection{Developing the Pipeline}
The \emph{Augraphy} library presents an easy-to-use API for constructing feature pipelines, which has been designed for interoperability with other augmentation tools, and within the broader data ecosystem.
While \emph{Augraphy}'s default pipeline has what we believe to be quite realistic defaults, we wanted a broader range of features from this dataset than those the default pipeline could produce.
To address this, we broke all of the parameters for every augmentation constructor out into separate variables, tweaking these and committing the new pipeline to GitHub.
We created an automated daily build in GitHub Actions to render a random selection of ground-truth images with the updated pipeline, then our team met frequently to discuss the output and make adjustments to the augmentation parameters, until we were consistently satisfied with the results.

@@

Five individuals were recruited for this task, which involved printing 40 pages of documents and manually applying various effects such as folds, wrinkles, smudges, highlighters, pencils, crayons, splatters of ink or other liquids, printing, scanning, faxing and other creative and reasonable treatments determined by these workers.
The process continued over a period of two weeks, incurring a cost of approximately $1,000 USD.
While there are plenty of opportunities to streamline the operation, scaling this process is expensive in terms of both time and money, and may have unpredictable results.

@@

\begin{table}[]
    \centering
    \caption{Document image denoising cross-test performance of NAFNet models trained on \emph{ShabbyPages} and \emph{NoisyOffice}.}
    \scalebox{0.9}{
    \begin{tabular}{lll}
    \toprule
    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~}\\
        \midrule
        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & \textbf{0.96}\\
        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.83\\
        \bottomrule
    \end{tabular}}
    \label{tab:denoising_results}
\end{table}

As can be seen from Table \cite{tab:denoising_results}, the \emph{ShabbyPages}-trained denoiser generalized to \emph{NoisyOffice} far better than the \emph{NoisyOffice}-trained model generalized to \emph{ShabbyPages}. This result is consistent with the much higher diversity present within the \emph{ShabbyPages} set, relative to features found in the \emph{NoisyOffice} database.

@@

Multiple common image processing metrics were applied to the predictions made by each model, comparing these to the preprocessed groundtruths.
In addition to the structural similarity metric from the denoising task, we add the peak signal to noise ratio (PSNR) and the root mean squared error (RMSE). Both of these metrics are more useful for determining the differences between binary images: together, they give some idea of the degree to which noise artifacts remain in the image after denoizing and binarization affect the visual signal, and how many such artifacts exist.
The averages of each metric over all predictions was taken, with the results presented in Table \cite{tab:binarization_results}.

\begin{table}[]
    \centering
    \caption{Document image binarization performance of a NAFNet model trained and tested on \emph{ShabbyPages} and \emph{NoisyOffice}.}
    \scalebox{0.9}{
    \begin{tabular}{lllll}
    \toprule
    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{PSNR$\uparrow$~} \textbf{RMSE$\downarrow$~}\\
        \midrule
        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & \textbf{0.947} & \textbf{38.098} & \textbf{3.205}\\
        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.811 & 34.562 & 5.384\\
        \bottomrule
    \end{tabular}}
    \label{tab:binarization_results}
\end{table}

>>>>

\subsection{Developing the Pipeline}
The \emph{Augraphy} library presents an easy-to-use API for constructing data augmentation pipelines for document images, which has been designed for interoperability with other augmentation tools, and within the broader data ecosystem.
While \emph{Augraphy}'s default pipeline has what we believe to be quite realistic defaults, we wanted a broader range of features from this dataset than those the default pipeline could produce.
To address this, we broke all of the parameters for every augmentation constructor out into separate variables, tweaking these and committing the new pipeline to GitHub.
We created an automated daily build in GitHub Actions to render a random selection of ground-truth images with the updated pipeline, then our team met frequently to discuss the output and make adjustments to the augmentation parameters, until we were consistently satisfied with the results.

@@

Five individuals were recruited for this task, which involved printing 40 pages of documents and manually applying various effects such as folds, wrinkles, smudges, highlighters, pencils, crayons, splatters of ink or other liquids, printing, scanning, faxing and other creative and reasonable treatments determined by these workers.
The process continued over a period of two weeks, incurring a cost of approximately \$1,000 USD.
While there are plenty of opportunities to streamline the operation, scaling this process is expensive in terms of both time and money, and may have unpredictable results.

@@

\begin{table}[]
    \centering
    \caption{Document image denoising cross-test performance of NAFNet models trained on \emph{ShabbyPages} and \emph{NoisyOffice}.} \label{tab:denoising_results}
    \scalebox{0.9}{
    \begin{tabular}{lll}
    \toprule
    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~}\\
        \midrule
        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & \textbf{0.96}\\
        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.83\\
        \bottomrule
    \end{tabular}}
\end{table}

As can be seen from Table~\ref{tab:denoising_results}, the \emph{ShabbyPages}-trained denoiser generalized to \emph{NoisyOffice} far better than the \emph{NoisyOffice}-trained model generalized to \emph{ShabbyPages}. This result is consistent with the much higher diversity present within the \emph{ShabbyPages} set, relative to features found in the \emph{NoisyOffice} database.

@@

Multiple common image processing metrics were applied to the predictions made by each model, comparing these to the preprocessed groundtruths.
In addition to the structural similarity metric from the denoising task, we add the peak signal to noise ratio (PSNR) and the root mean squared error (RMSE). Both of these metrics are more useful for determining the differences between binary images: together, they give some idea of the degree to which noise artifacts remain in the image after denoizing and binarization affect the visual signal, and how many such artifacts exist.
The averages of each metric over all predictions was taken, with the results presented in Table~\ref{tab:binarization_results}.

\begin{table}[]
    \centering
    \caption{Document image binarization performance of a NAFNet model trained and tested on \emph{ShabbyPages} and \emph{NoisyOffice}.}
    \scalebox{0.9}{
    \begin{tabular}{lllll}
    \toprule
    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{PSNR$\uparrow$~} & \textbf{RMSE$\downarrow$~}\\
        \midrule
        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & \textbf{0.947} & \textbf{38.098} & \textbf{3.205}\\
        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.811 & 34.562 & 5.384\\
        \bottomrule
    \end{tabular}}
    \label{tab:binarization_results}
\end{table}
